\documentclass[10pt, letter]{article}

% This is a tex file to make Chuwen's CV.
% The content is 

\usepackage{jk-vita}
\usepackage[notes,natbib,isbn=false,backend=biber,url=false,numbermonth=true]{biblatex-chicago}

%\usepackage{biblatex}

% Your biblatex file is likely somewhere else.
\addbibresource{ref.bib}

\title{}
\name{Chuwen Zhang}
% I guess postnoms is like junior? I dunno.
\postnoms{}
\address{
    }
  
    
    \email{chuwzhang@gmail.com}
    
    \tel{(+86) 13227265529}
    
    
    \github{github.com/brentian}
    
    \wechat{brentian}
    \subject{}
  
\begin{document}
\maketitle


\section{Education}
% Education uses a different field called ``items.''
\subsection{The University of Texas at Austin \\
  \bullet \quad M.S. in Operations Research, June 2017}
% Store certain things in a field called 'text' to allow another field
% for priority.
\textit{Major fields in mixed integer programming and applications in
supply chain management.} \\
% Store certain things in a field called 'text' to allow another field
% for priority.
\textit{Advisor, Jonathan F. Bard} \\
\subsection{Shanghai Jiao Tong University \\
  \bullet \quad B.E. in Industrial Engineering, June 2015}

\section{Professional Experience}

\subsection{Cardinal Operations, Algorithm Engineer (Operations
Research)}
\texttt{September 2018 - Present} \\
\underline{\textit{Large-scale MILP algorithm design for production
planning}} \\
\bullet\quad Developed a very large-scale (17m constraints and 19m
variables) planning model for a global ICT gaint to tackle difficulties
in delivery requirements and to maintain a favorable service level. \\
\bullet\quad Designed an LP-based iterative framework to decompose the
full problem via various pre and post processing techniques, graph-based
heuristics to deal with integral and hard features. The model has been
deployed and used in real production. \\
\bullet\quad Extended the model as a S\&OP and APS product tailored for
manufacturing industry. The product has been used in projects with other
industry leaders. \\
\underline{\textit{Planning models for air-cargo operation}} \\
\bullet\quad Designed optimization algorithms for an air-cargo operation
problem in a global courier company. Implemented MILP, mixed integer
SOCP programs for the upper-level aircraft parking problem, and
heuristic based scheduling algorithms to operate cargo trucks to
minimize the total transferring distance and total operation time. \\
\bullet\quad Applied a geometric rounding scheme for the assignment
constraints to achieve a 10\% optimality gap comparable to 8\% gaps
obtained by mixed integer solvers for a static planning horizon of 24
hours. \\
\bullet\quad Established approaches for dynamic and DRO extension (under
uncertain plane arrival time and transferring time) from the static
assignment problem. Based on simulation results, the position
assignments by DRO approach reduces total operation time to 1.4 hours
compared to over 2 hours on average from the historical data in every
2-hour evaluation slice. \\
\underline{\textit{Other notable projects}} \\
\bullet\quad Designed optimization algorithms for one of China's ``Big
Three'' airlines to decrease immense engine maintenance costs. The model
is to generate optimal repair plans for engines within the entire fleet,
to ensure high service levels, and to minimize zero-backup risks under
stochastic damage development and uncertain failure events captured by
the distributional robust approach. \\
\bullet\quad Participated in: unit commitment problem with National
Grid, fabrication ordering scheduling with the COMAC, etc. \\
\subsection{RTBAsia, Data Scientist}
\texttt{September 2017 - August 2018} \\
\underline{\textit{Machine learning models for advertising fraud
detection}} \\
\bullet\quad Developed an offline ML pipeline on the Spark platform by
learning from real-time advertising bidding logs to differentiate
invalid traffic. \\
\bullet\quad Created streaming models that evaluate the user behavior on
the client websites by visiting graph and click or touch events
generated via JavaScript. The model is able to recognize invalid traffic
using disguised Ad IDs via CV-like features implemented in TensorFlow
and Kafka. The JS user identification approach has then become the
industry standard under regulation of GDPR in 2018. \\
\bullet\quad Researched on DL-based (CV + NLP) models to evaluate Ad
context (URL, for example) for digital marketing, and to protect brands
from unsafe, inappropriate, or incompatible content. \\

\section{Skills}

Proficient: Python, Julia, Pandoc, Scala\\[.15cm]
Past experience/collaborative use: C++, HTML5/CSS, Unix, Haskell,
JavaScript, LaTeX, TensorFlow\\[.15cm]
Modeling: JuMP, Mosek, Gurobi, COPT, CLP, Spark ML\\[.15cm]
Summary: proficient in linear, conic, and mixed integer optimization,
and methods for large scale applications with real-world practice.
Familiar with common machine learning algorithms and experienced in
modeling pipeline in big data environment.\\[.15cm]

\section{Publications}
\cite{zhang2017controlling} \\[.15cm]



\end{document}
